---
title: "Scottsdale Energy Consumption 2020"
output: html_notebook
---
# Importing and Cleaning the Data
We first import the data as `raw`. We want to ensure that the data is formatted properly. The formatted data will be stored in the variable `d`. 
```{r import-data}
raw <- read.csv("https://www.phoenixopendata.com/
dataset/598be280-a5ce-4c77-b802-321756332dfb/
resource/d49c88c7-93b4-4c83-9032-31e4fd620f61/
download/20210519_opendata-1.csv")

d <- raw
```

### Renaming the columns
We notice that the column names contain periods ("`.`"). These periods could cause issues with our code, since `.` is a special operator. Therefore, we replace the periods with underscores ("`_`"). While we're at it, we make the column names lowercase for typing ease and code consistency.
```{r rename-cols}
print(colnames(d))      # Print the column names.

# Rename the columns.
colnames(d) <- tolower(gsub(".", "_", colnames(raw), fixed = TRUE))
```

## Removing unneeded data 
We notice that the year is all the same, so we remove that column.
```{r remove-year-col}
unique(d$year)  # View all unique year values.

# Remove the year column by setting it to NULL.
d$year <- NULL
```

We also see that there is a column denoting the electricity provider; we are only interested in the energy usage, so we will remove that column.
```{r remove-utility-co-col}
d$electric_utility <- NULL
```

### Formatting columns 
Let us observe what our data looks like.
```{r str-d}
str(d)
```

#### Latitude and longitude columns 
We immediately notice that the latitude and longitude, which should contain numerical data only, are stored as characters. Let's take a look at why.
```{r lat-long}
print(unique(d$latitude))
print(unique(d$longitude))
```

There seem to be blank rows and rows filled with "N/A". Which sites do these belong to? 
```{r blank-lat-long}
subset(
        d,
        latitude == "" | longitude == "" |
        latitude == "N/A" | longitude == "N/A"
)
```
The sites fall into one of two categories:
1. The site has multiple locations (e.g. Streetlights, Traffic Signals). 
2. The site belongs to the Goodyear Airport. 

There is **one** exception: the PHX SkyTrain Switch Yard does not belong to either of the two categories, but it has both latitude and longitude set as "N/A". 

For now, we will set all of these sites to having `latitude = longitude = NA`-- we can add in geographical coordinates to those sites that lie in only a single location later. 

```{r}
# Note: Latitude = "" (or = "N/A") iff longitude = "" (or = "N/A")
d[d$latitude == "" | d$latitude == "N/A", c("latitude", "longitude")] <- NA

d$latitude <- as.numeric(d$latitude)
d$longitude <- as.numeric(d$longitude)
```
#### Building type column 
```{r}
unique(d$building_type)
```
We notice that we have building types "N/A" and " N/A ". Let's change those strings to the value `NA`. In addition, the letter casing is inconsistent, so let us convert it to lowercase.  
```{r}
d[
        d$building_type == "N/A" | d$building_type == " N/A ",
        c("building_type")
] <- NA
d$building_type <- tolower(d$building_type)
```

```{r}
# d[c("site_name")]

# Want to (1) remove unneeded variables
# (do natural gas, solar, etc. usage add up to electricity_usage?)
# Relationship between building type and department?
# (Now that Im typing, obviously the answer is yes.)
```


<!-- #### Energy use intensity column 
We notice that there are many `NA` values for `energy_use_intensity`. Let's take a look at the sites where `energy_use_intensity = NA`. -->
```{r}
print(paste("IGNORE",
        dim(subset(d, is.na(energy_use_intensity)))[1],
        "of",
        dim(d)[1],
        "rows have energy_use_intensity = N/A."
))
```
<!-- Nearly half of the rows have null energy use intensities; there is not a meaningful amount of data to be able to perform analysis on energy use intensity, so let us get rid of the data.  -->
```{r}
# d$energy_use_intensity <- NULL
``` 