# Analysis
Now we have properly formatted the data that is needed to explore electricity usage. 
```{r, include = FALSE}
source("00_import_clean.r", local = knitr::knit_global())
```

## Initial Observations 
```{r}
summary(d)
```
## Electricity Usage 
* **current_solar**: Peak capacity in kW of solar panels installed at site. 
* **natural_gas_usage**: Total annual natural gas consumption at site in therms. 
<!-- 
# Relationship between building type and department?
# (Now that Im typing, obviously the answer is yes.) --> 
```{r}
elec <- d$electricity_usage
p <- hist(elec)
```
We have one large bar and at least 3 tiny bars-- clearly the outliers are large. We can see this clearly in a boxplot, where the outliers are defined as any values 1.5*IQR outside the first and third quartiles. 
```{r}
bp <- boxplot(elec)
```

```{r, include = FALSE}
summary(elec)
iqr_elec <- IQR(elec)
```

Let's take out the outliers. 
```{r}
elec_mid <- setdiff(elec, bp$out)
boxplot(elec_mid)
hist(elec_mid)
```
We now have a more reasonable distribution. The distribution still is heavily skewed towards the lower end-- that means that there are many sites that require very little energy (< 50,000 kW/yr) and fewer sites that require large amounts of energy. 

Let us try to find where the outliers belong.
```{r}
par(mfrow = c(2, 1))
bp_all <- boxplot(electricity_usage ~ department, data = d, las = 2)

boxplot(electricity_usage ~ building_type, data = d, las = 2)
```

We first note that the Water department has a significantly higher energy usage than any other department.
```{r}
subset(d, department == "Water")
```

Looking at the data, we see that the Water department contains only one data point, the Water Services Department. The entire water services department is captured in a single data point rather than separated by building.

What if we drop that department?
```{r}
bp_all <- boxplot(electricity_usage ~ department,
        data = d[d$department != "Water", ], las = 2
)
```
Now Aviation has the most outliers, which is what we expected.


Does electricity usage relate to building area?
```{r}
par(mfrow = c(1, 1))
with(d, plot(building_area, electricity_usage))
with(d, cor(building_area, electricity_usage))
```
We expected the correlation to be much higher. Perhaps there is a stronger relationship between electricity usage and department or building type. 
<!-- Compare the outliers energy usage to everything else? -->

