# Traffic signals and Energy Usage of Public Buildings in Scottsdale
We would like to compare the energy usage of the traffic signals in Scottsdale to the energy usage of other buildings.

Energy usage data is taken from Scottsdale Open Data. We import and clean this data in `00_import_clean.r`, and we store the streetlight-specific data in `signals`.
```{r}
# Import the data.
source("00_import_clean.r", local = knitr::knit_global())
  # raw == raw data 
  # d == formatted data

# Streetlight data.
signals <- subset(d, site_name == "Traffic Signals")
```

Now let's take a look at the sites that use less energy than a traffic signal.
```{r}
par(mfrow = c(1, 1))
barplot(
  subset(elec_mid, elec_mid < est[1] | elec_mid < est[2]),
  ylim = c(0, 27000)
) # ELEC_MID IS DEFINED IN 01 NB.
abline(h = est[1], col = "red")
abline(h = est[2], col = "blue")
text(
  20,
  y = c(est[1], est[2]) + 1000,
  labels = c("200 traffic signals", "300 traffic signals"),
    cex = 0.8,
    col = c("red", "blue")
 )
```

Now we want to get the buildings that use less energy than the traffic signals.
```{r}
bldgs_lt_sigs <- subset(d, d$electricity_usage < est[2])

t <- bldgs_lt_sigs[,c("site_name","electricity_usage","department","building_type")]
```

```{r}
t
```
The buildings that use less energy than a single traffic signal are not all that out there. they are parks, buildings that don't seem to use that much energy. How about comparing energy usage for all traffic signals?

## Energy usage compared to the total energy usage of traffic signals.
```{r}
elec_sigs <- signals$electricity_usage # Electricity usage of all signals

# Buildings minus traffic signals 
d_no_sigs <- subset(d, site_name != "Traffic Signals")

# Plot 
barplot(
  d_no_sigs$electricity_usage 
)
abline(h = elec_sigs, col = "blue")
text(
  20,
  y = c(est[1], est[2]) + 1000,
  labels = c("Energy Usage of Traffic Signals"),
    cex = 0.8,
    col = c("red")
 )
```

Now I want the sites whose energy usage is less than the usage of the traffic signals. 

```{r}
d_less_than_sigs <- subset(d_no_sigs, electricity_usage <= elec_sigs)

d_less_than_sigs[order(d_less_than_sigs$electricity_usage, decreasing = TRUE),]  
```

Typical household 11,000 kW hours / year (https://www.eia.gov/energyexplained/use-of-energy/electricity-use-in-homes.php)
```{r}
# Energy usage per square foot of buildings

```

```{r}
d_more_than_sigs <- subset(d_no_sigs, electricity_usage > elec_sigs)

d_more_than_sigs[order(d_more_than_sigs$electricity_usage),]
```